On Sample Size for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2023-08-21 Manuscript/manuscript.tex
suggestions on simulation result summari

\paragraph{A Proposed CI}
We propose a CI that is centered at the point estimator and uses the variation
in the bootstrap estimates to construct the error bound. This interval requires
the computation of $\bar\theta_n^{(b)}$, the mean of all bootstrap point
estimates, and $\widehat{\text{bias}} = \bar\theta_n^{(b)} - \hat\theta_n$.
A $(1 - \alpha)100\%$ CI is
\[
(\hat\theta_{n, \alpha/2}^{(b)} - \widehat{\text{bias}}, \quad
\hat\theta_{n, 1 - \alpha/2}^{(b)} - \widehat{\text{bias}}).
\]
This CI is centered around $\hat\theta_n$ and can also be rewritten
as 
\[
(\hat\theta_n + \hat\theta_{n, \alpha/2}^{(b)} - \bar\theta_n^{(b)}, \quad
\hat\theta_n + \hat\theta_{n, 1 - \alpha/2}^{(b)} - \bar\theta_n^{(b)}).
\]
It is asymmetric, as different critical values are used to compute
the lower and upper bounds.

@@

Based on Figure~\ref{fig:mu}, Student's $t$ seems to generally
be the best method for estimating $\mu$.
For $\phi = -0.4$, Student's $t$ CIs over-cover 
$\mu$ for smaller $n$, whereas other CIs recover $\mu$ at the
nominal rate for all $n$ observed. For 
$\phi = -0.2$, 
all CIs recover $\mu$ at the nominal rate for all $n$. For $\phi = 0$, or when the 
sample is independently normally distributed, $n \geq 200$ seems to 
be large enough to recover $\mu$ at the nominal rate when using any CIs
 besides Student's $t$ CIs, which seem to recover $\mu$ at the nominal rate for
  all $n$.
For $\phi = 0.2$, $n \geq 800$ seems to be sufficient to recover $\mu$
at the nominal level when using
any CIs besides Student's $t$ CIS, which recover $\mu$ at the nominal
 rate for all $n \geq 200$.
For $\phi = 0.4$, $n \geq 3200$ seems to be large enough to recover $\mu$
at the nominal level when using
any CIs besides Student's $t$ CIS, which seem to recover $\mu$ at the nominal
 rate for all $n \geq 800$.

>>>>

\jy{Can we come up with a good name for the proposed method? Other people may cite this.}
\paragraph{A Proposed CI}
We propose a CI that is centered at the point estimator and uses the variation
in the bootstrap estimates to construct the error bound. This interval requires
the computation of $\bar\theta_n^{(b)}$, the mean of all bootstrap point
estimates, and $\widehat{\text{bias}} = \bar\theta_n^{(b)} - \hat\theta_n$.
A $(1 - \alpha)100\%$ CI is
\[
(\hat\theta_{n, \alpha/2}^{(b)} - \widehat{\text{bias}}, \quad
\hat\theta_{n, 1 - \alpha/2}^{(b)} - \widehat{\text{bias}}).
\]
This CI is centered around $\hat\theta_n$ and can also be rewritten
as 
\[
(\hat\theta_n + \hat\theta_{n, \alpha/2}^{(b)} - \bar\theta_n^{(b)}, \quad
\hat\theta_n + \hat\theta_{n, 1 - \alpha/2}^{(b)} - \bar\theta_n^{(b)}).
\]
It is asymmetric, as different critical values are used to compute
the lower and upper bounds.

@@

\jy{The results discussion need to be streamlined. The three paragraphs are too
  similar, and only student's ci is discussed. Questions to consider:
  1) which methods give the right coverage as sample size increases?
  2) which methods needs smaller sample sizes to get the right coverage?
  3) what's the difference between the results in positive and negative
  dependence?
  4) how does the result change as dependence gets stronger?
  }

For estimating the mean parameter~$\mu$,
Figure~\ref{fig:mu} suggests that the Student's $t$ interval is the best method.
For $\phi = -0.4$, Student's $t$ CIs over-cover 
$\mu$ for smaller $n$, whereas other CIs recover $\mu$ at the
nominal rate for all $n$ observed. For 
$\phi = -0.2$, 
all CIs recover $\mu$ at the nominal rate for all $n$. For $\phi = 0$, or when the 
sample is independently normally distributed, $n \geq 200$ seems to 
be large enough to recover $\mu$ at the nominal rate when using any CIs
 besides Student's $t$ CIs, which seem to recover $\mu$ at the nominal rate for
  all $n$.
For $\phi = 0.2$, $n \geq 800$ seems to be sufficient to recover $\mu$
at the nominal level when using
any CIs besides Student's $t$ CIS, which recover $\mu$ at the nominal
 rate for all $n \geq 200$.
For $\phi = 0.4$, $n \geq 3200$ seems to be large enough to recover $\mu$
at the nominal level when using
any CIs besides Student's $t$ CIS, which seem to recover $\mu$ at the nominal
 rate for all $n \geq 800$.
